\documentclass{article}
\title{Spheres}
\author{Jaime E. Forero-Romero}
\begin{document}
\maketitle
\begin{abstract}

Gravity is the dominant force shaping the spatial distribution of galaxies in
the Universe. Under the assumption of homogeneity and isotropy of the Universe
beyond a certain physical scale one can usually approximate the local
kinematic evolution of galaxy by the matter distribution below that
homogeneity scale. In this letter we show that if the matter
distribution is composed by a discrete set of points then, due to
statistical fluctuations, the influence of matter has a measurable
effect at all scales. Our results are based on straightforward
analytical considerations, monte-carlo realizations and the analysis
of cosmological N-body simulations. We discuss the implications of
these results in the interpretation of the peculiar motion of our
galaxy. We suggest possible cosmological tests of these ideas for
future observational facilities. 



\end{abstract}

1. Of all the fundamental forces gravity plays the dominant role in
defining the large scale structure of the Universe. From very
homogeneous conditions gravitational instability drives the emergence
of a web-like pattern. The influence of
matter beyond that scale can be discarded on the grounds that
the net gravitational force inside an homogeneous spherical
shell is zero. [Inhomogeneity, Kirchoff's theorem] [...]



2. Large galaxy surveys help us to define different physical scales for
homogeneity [...]


3. We consider first a simple phenomenological model where matter is
homogeneously distributed over the surface of a sphere of radius
$R$. This distribution consists of a set of $N$ point masses with mass
$m$. [...] This shows that the total force, $F_{\rm T}$, inside that spherical
distribution can be expressed as follows in terms of the force $F_{\rm
m}(R)$ produced by each point mass placed at a position $R$:

\begin{equation}
F_{\rm T } = N^{1/2} F_{\rm m} (R),
\end{equation}

This has been derived before [http://arxiv.org/pdf/0903.1355v1.pdf].


4. Conventional approximations consider that the net gravitational force
inside an statistically homogeneous shell matter distribution is
zero. However, by extending the result we have just derived, as long
the matter distribution is discrete, this result does not hold. We can
now extend this result for an statistically homogeneous distribution
of points.[...] We run again a simple Monte Carlo simulation to find
that the total force produced by the particle distribution is twice as
the of a single mass $m$ located at a distance $R_{\rm s}$ equal to
the average interparticle setup, independent of the total number of
particles. 

\begin{equation}
F_{\rm T} = 2 F_{\rm m}(R_{\rm s}).
\end{equation}

5. In the case of the actual large scale matter distribution in the
Universe, galaxies are found to have two distinct characteristics with
respect our toy model. First, the galaxies are not randomly
distributed, but clustered. Second, the galaxies span a wide range of
masses, with less massive galaxies being more common than massive
galaxies. In order to test the influence of these two carachteristics
we use a large comological N-body simulation.[...]

6. The results of the simulation [...] 

7. We also consider the variation in the direction of the net force
when the positions of the halos are perturbed within 1 $h^{-1}$ which
is the typical lnghtscale that these objects are expected to travel in
the age of the Universe.


8. The fact that our simple analytical model describes the result
obtained by simulations strenghtens our interpretation on the basis of
fundamental point processes. [...]

9. The velocity of our galaxy in the rest-frame of the cosmic
micriwave background is 627 km
s$^{-1}$. [http://arxiv.org/pdf/1109.3856v1.pdf]. It has been inferred
that the $382$ km s$^{-1}$ are induced by the mass distribution within
$R=30$ $h^{-1}$ Mpc, we call this the local component. This gives a
net result of 382 km s$^{-1}$ that must be induced by the matter
distribution from matter with positions beyond $R$, this is referred
as the tidal component.  Both components, local and tidal, are
pointing in the same direction (??? SURE ??).[...]

10. The effects of the net force imposed by the matter distribution
in the Universe is also in principle detectable in systems isolated 
from massive structures. The most interesting case would be the
kinematic evolution of galaxies located in large scale voids. In these
regions the dominant gravitational interaction would be provided by
the tidal component and not by nearby
structures. [http://adsabs.harvard.edu/abs/2011IJMPS...1...41V] 

11. [Implications for local group mass estimates in the timing argument]

12. Possible effects on detailed methods that seek to infer local
density modes from redshift measurements. 

13. The physics of this effect are very simple to interpret.








\end{document}
